Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-12 TACAS2018/paper.tex
Some refining of the intro

The coarse synthesiser uses a low resolution discretized model of a 
transformation of the original model. Furthermore, it only looks initially at
static properties  of the system. This largely reduces the complexity of
the problem, enabling the synthesiser to offer fast response times. If any 
of these parameters is inadequate, the refinement loop will supply a better
abstraction to obtain a feasible answer.
Due to either numerical imprecision or overapproximations, the candidate
solution presented by the first synthesiser will likely not meet the spec. A 
second synthesiser, with a much more precise refinement including a 
mapping between the real and transformed spaces will create a candidate
solution that is more adequate to the real model. This second stage uses
perturbation analysis and therefore requires an initial solution to operate.
If the second synthesiser is unable to find a candidate solution, it will cue
the modeller to supply a finer abstraction to the coarse synthesiser which
will in turn provide a better candiate to the second stage.
The combined synthesisers are thus capable of reasoning about complex
models with high computational efficiency due to their modularity.

%The synthesiser uses a discrete time model that relates to the sampling
%time.  It begins with a very simple abstraction of the real system which
%only considers the static properties of the model.  It~also uses a very low
%precision bit vector representation of the real dynamics in order to
%minimise synthesis time.  
A candidate solution is then passed to a set of verifiers which will
evaluate the synthesised controller over an even more precise
abstraction of the concrete domain in both discrete and continuous
space/time.  This stage uses abstraction refinement when needed to ensure
that rejected candidates are not being discarded due to the
over-approximation.

\todo{remove until end of enumerate}
The nature of the counterexamples varies depending on
the following conditions:
%
\begin{enumerate}
%
\item Initially, we look for possible errors caused by the restricted domain
of the synthesisers (e.g., overflows and rounding).  These will typically 
manifest in the static properties of the system. If an error is found, the
modeller is signalled to increase the precision of the synthesisers.
%
\item Next we explore the nature of the discrete-time progression to mark
a counterexample that relates to the progression of the system. If such a
counterexample exists, we indicate its initial conditions and time horizon,
thus instructing the synthesiser to refine its abstraction with respect to the
set of initial states and number of iterations. 
%
\item Continuous time analysis indicates the need for decreasing the
sampling time due to continuous excursions outside the safety region in
between samples.  This changes the problem statement of the synthesiser to a
new discrete-time model.
%
\item A final condition arises when a candidate solution cannot be found,
thus requiring higher precision of the abstraction numerical representation. 
We initially consider the plant representation to be too conservative and
may eventually increase the controller FWL specification when no controller
can be found for a given precision.
%
\end{enumerate}

>>>>

We make use of a two-stage counterexample-guided inductive
synthesis (CEGIS) driven by abstraction refinement.
The first, coarse, synthesis stage uses a low resolution discretized model of a 
transformation of the original model. Furthermore, it only looks initially at
static properties  of the system. This largely reduces the complexity of
the problem, enabling the synthesiser to offer fast response times. %% If any 
%% of these parameters is inadequate, the refinement loop will supply a better
%% abstraction to obtain a feasible answer.
Due to either numerical imprecision or overapproximations, the
candidate solution presented by the first synthesiser will likely not
meet the spec. A second synthesis stage, with a much more precise
refinement including a mapping between the real and transformed spaces
will create a candidate solution that is more adequate to the real
model. This second stage uses perturbation analysis and therefore
requires an initial solution to operate.  Whenever the second stage is
unable to find a candidate solution, it triggers an abstraction
refinement phase, resulting in a finer abstraction being fed back to
the first stage.  The combined synthesisers are thus capable of
reasoning about complex models with high computational efficiency due
to their modularity.

%The synthesiser uses a discrete time model that relates to the sampling
%time.  It begins with a very simple abstraction of the real system which
%only considers the static properties of the model.  It~also uses a very low
%precision bit vector representation of the real dynamics in order to
%minimise synthesis time.  
A candidate solution is then passed to a set of verifiers which will
evaluate the synthesised controller over an even more precise
abstraction of the concrete domain in both discrete and continuous
space/time.  The verification phase uses abstraction refinement when needed to ensure
that rejected candidates are not being discarded due to the
over-approximation.

%% The nature of the counterexamples varies depending on
%% the following conditions:
%% %
%% \begin{enumerate}
%% %
%% \item Initially, we look for possible errors caused by the restricted domain
%% of the synthesisers (e.g., overflows and rounding).  These will typically 
%% manifest in the static properties of the system. If an error is found, the
%% modeller is signalled to increase the precision of the synthesisers.
%% %
%% \item Next we explore the nature of the discrete-time progression to mark
%% a counterexample that relates to the progression of the system. If such a
%% counterexample exists, we indicate its initial conditions and time horizon,
%% thus instructing the synthesiser to refine its abstraction with respect to the
%% set of initial states and number of iterations. 
%% %
%% \item Continuous time analysis indicates the need for decreasing the
%% sampling time due to continuous excursions outside the safety region in
%% between samples.  This changes the problem statement of the synthesiser to a
%% new discrete-time model.
%% %
%% \item A final condition arises when a candidate solution cannot be found,
%% thus requiring higher precision of the abstraction numerical representation. 
%% We initially consider the plant representation to be too conservative and
%% may eventually increase the controller FWL specification when no controller
%% can be found for a given precision.
%% %
%% \end{enumerate}
